%-------------------------
% Resume in Latex
% Author : Kshitij Betwal (based on Jake Gutierrez's template)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Balanced margins: fills page comfortably without overflow
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.15in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-6pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Kshitij Betwal} \\ \vspace{1pt}
    \small Bengaluru, India $|$ +91 9558412620 $|$ \href{mailto:kshitij.betwal@gmail.com}{\underline{kshitij.betwal@gmail.com}} $|$
    \href{https://linkedin.com/in/kshitijbetwal}{\underline{linkedin.com/in/kshitijbetwal}} $|$
    \href{https://github.com/theNeuralHorizon}{\underline{github.com/theNeuralHorizon}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{CS undergrad (AI specialization) shipping production ML and backend systems end-to-end. Recent work spans deployed microservices on Render and Vercel, on-device neural networks for Android, and financial analytics pipelines on PostgreSQL + Power BI. Strong in Python, C++, TypeScript, system design, and model-to-API delivery on AWS.}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Manipal Institute of Technology}{Bengaluru, India}
      {B.Tech in Computer Science (Artificial Intelligence); CGPA: 7.5/10}{2023 -- 2027}
      \resumeItemListStart
        \resumeItem{\textbf{Coursework:} Data Structures \& Algorithms, OOP, DBMS, System Design, Operating Systems, Computer Architecture, Distributed Systems, Machine Learning.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Zeoxia}{Remote}
      {Builder Resident (R\&D) -- Builder Residency v1}{Jan 2026 -- Present}
      \resumeItemListStart
        \resumeItem{Prototyping AI and edge-computing features end-to-end, shipping internal tooling the R\&D team uses to cut model-validation turnaround.}
        \resumeItem{Designed experimentation workflows compressing the iterate-eval-ship loop, accelerating production readiness for new model checkpoints.}
        \resumeItem{Built internal developer tooling (CLI + dashboards) that eliminated repetitive setup and freed senior engineer cycles for deep work.}
        \resumeItem{Authored technical research notes feeding architecture decisions; mentored 1:1 by senior engineers on shipping production-grade deep-tech products.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Predictive Maintenance System} $|$ \emph{FastAPI, React, Scikit-learn, Docker, Render, Vercel} $|$ \href{https://predictive-maintenance-system-two.vercel.app}{\underline{Live Demo}}}{Feb 2026}
          \resumeItemListStart
            \resumeItem{Deployed a decoupled microservices app (FastAPI backend on Render, React frontend on Vercel, Docker-built) serving real-time failure prediction on industrial sensor telemetry.}
            \resumeItem{Trained Random Forest (binary classification) + Isolation Forest (unsupervised anomaly detection) on the AI4I 2020 dataset; inference exposed via Pydantic-validated REST endpoints.}
            \resumeItem{Implemented GitHub OAuth2 + JWT stateless authentication with Authlib and strict cross-origin CORS between Render and Vercel for secure, portable API access.}
            \resumeItem{Containerized the full stack with Docker Compose for reproducible local development mirroring the production Render + Vercel cross-origin topology.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{FakeCallShield -- On-Device AI Scam-Call Detector} $|$ \emph{React Native, Kotlin, TypeScript, Python, Scikit-learn}}{Apr 2026}
          \resumeItemListStart
            \resumeItem{Engineered an Android app classifying AI-generated and spoofed calls \textbf{100\% on-device} (zero network) with MLP inference in \textbf{under 20 ms per 3-second chunk}.}
            \resumeItem{Extracted a \textbf{104-feature acoustic vector} (MFCC + delta + delta-delta, jitter, shimmer, HNR, phase continuity) in pure TypeScript, avoiding TensorFlow/ONNX on mobile.}
            \resumeItem{Trained a 104-256-128-64-1 MLP with Scikit-learn on 10,000 samples; calibrated decision thresholds from ROC analysis (Youden's J) instead of hardcoded cutoffs.}
            \resumeItem{Integrated Android \texttt{CallScreeningService} + STIR/SHAKEN into a multi-signal risk score (attestation 40\%, contact 30\%, timing 15\%, voice ML 15\%) within the 5-second OS deadline.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Credit Card Financial Dashboard} $|$ \emph{Power BI, DAX, SQL, PostgreSQL, Docker}}{Feb 2026}
          \resumeItemListStart
            \resumeItem{Analyzed \textbf{10,000+ transactions} from a Dockerized PostgreSQL source in Power BI across card tier, region, job profile, transaction mode, and season.}
            \resumeItem{Authored DAX measures for live revenue, interest, and utilization KPIs, \textbf{cutting reporting latency 30\%} versus the prior spreadsheet workflow.}
            \resumeItem{Surfaced \textbf{\$47M revenue concentration} in mid-tier cards, a \textbf{Q4 \$806M} transaction surge, and \textbf{\$13M TX/NY} geographic risk, reshaping product strategy.}
            \resumeItem{Built a reproducible SQL transformation layer against containerized Postgres, enabling the dashboard to refresh against new transaction snapshots without manual data prep.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, TypeScript, JavaScript, Kotlin, SQL (PostgreSQL, MySQL)} \\
     \textbf{ML / Data}{: PyTorch, Scikit-learn, Pandas, NumPy, MLflow, Power BI, DAX} \\
     \textbf{Backend / Systems}{: FastAPI, Node.js, REST APIs, Microservices, OAuth2/JWT, Docker, AWS (EC2, Cognito), CI/CD, Linux} \\
     \textbf{Frontend / Mobile}{: React.js, React Native (Expo), Tailwind CSS, Vite} \\
     \textbf{Concepts}{: DSA, OOP, System Design, Distributed Systems, MLOps}
    }}
 \end{itemize}

%-----------LEADERSHIP & ACHIEVEMENTS-----------
\section{Leadership \& Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{HackBricks 2026 (Databricks x Manipal)}: Shipped end-to-end ML drift and LLM hallucination monitoring under a 48-hour deadline. \\
     \textbf{Top 10, Honeywell Hackathon 2025}: Recognized for technical innovation in the real-time system-design track. \\
     \textbf{Google Hackathon Finalist}: Led a 5-person team to the final round out of 200+ competing teams. \textbf{LeetCode}: 70+ day daily streak across DSA topics.
    }}
 \end{itemize}

\end{document}
